An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-06-25 EconGrowth.Rnw
Changed height of clooud graph.

>>>>

Figure~\ref{fig:CDq_Cloud_Graph} shows $\alpha$, $\beta$, and $\gamma$ parameter values for resample models for the Cobb-Douglas model (with $q$). **** Need to add the sloped triangle lines if we decide to use graphs like this. ****

<<CDq_Cloud_Graph, fig.pos="H", fig.width=cdParameterGraphWidth, fig.height=ninePanelGraphHeight, fig.cap="Cobb-Douglas (with $q$) resample model parameters.", eval=TRUE>>=
cdeResampleTrianglePlot(energyType="Q")
@

**** Add triangle cloud plots for $x$ and $u$ if we decide to use these plots. ****
